\chapter{Innovative KPIs}
\label{ch:Innovative}
\section{Introduction on the Innovative KPIs}
\label{sec:Intro_Innvovative}
In the last few years there is a growing interest in the concept of sustainability and sustainable transportation. New technologies and new objective to be achieved make it necessary to define new indicators to measure new relevant aspects related to sustainability.

The fundamental role of sustainable development is also confirmed by the 2030 Agenda for Sustainable Development, adopted by all United Nations Member States in 2015. It provides a shared blueprint for peace and prosperity for people and the planet, now and into the future. 

The 2030 Agenda defines \emph{17 Sustainable Development Goals (SDGs)}\cite{sdgs} referred to different areas of social, economic and environmental development and each goal has specific objectives to be achieved over the next few years. 

In the following table the 17 SDGs are reported the ONU target in 2030 and the respective sustainability topics that can be faced in a public transport company.

\input{chapter/table_innovative/onu_2}

In order to better analyze these new aspects, the EU directive 2014/95\cite{directive201495eu} establishes that public interest companies, that meet a number of requirements, are required to provide a non-financial report. This annual sustainability report makes it possible to communicate the performance and sustainability impacts of a company. It consists of measuring, communicating and assuming responsibility towards stakeholders in relation to the performance of the organization with respect to the goal of sustainable development. The topic addressed in this report are:

\begin{itemize}
    \item Environmental topic
    \item Social and diversity equality topic
    \item Respect for human rights
    \item Anti-corruption and extortion
\end{itemize}

Given the importance of these new topics, the next paragraphs will be dedicated to identifying new indicators related to these new aspects. In particular, the \ref{sec:newtech} identifies the new technologies already on the market and other new technologies that are still in the research phase, but which will become more relevant in the future. Subsequently it is shown how new technologies and new data collected can lead to the definition of new indicators for green sustainability, social sustainability and maintenance.

Before identifying these new KPIs, it is good to remember the \emph{characteristics of a good indicator}.

First, indicators are measured to evaluate progress and they can be defined in terms of goals, objectives, targets and thresholds. For example, a planning process may involve establishing traffic congestion indicators (defining how congestion will be measured), goals (a desire for fast and efficient vehicle travel), objectives (changes in roadway supply or travel activity that reduces congestion) and targets (specific, feasible changes in congestion impacts or travel behavior that should be achieved), and thresholds (levels beyond which additional actions will be taken to reduce congestion).

Indicators can reflect various levels of analysis. For example, indicators may reflect the decision-making process (\textit{quality of planning}), responses (\textit{travel patterns}), physical impacts (\textit{emission and crash rates}), human and environmental effects (\textit{injuries and deaths, and ecological damages}), and their economic impacts (\textit{costs of crash and environmental damages}).
\newpage
Another way to classify the indicators in the following:
\begin{itemize}
    \item \emph{Process} the types of policies and planning activities, such as whether the organization has a process for collecting and publishing performance data, and public involvement.
    \item \emph{Inputs} the resources that are invested activities, such as the level of funding spent on various activities or modes.
    \item \emph{Outputs} direct results, such as the miles of sidewalks, paths and roads, and the amount of public transit service provided.
    \item \emph{Outcomes} ultimate results, such as the number of miles traveled and mode share, average travel speeds, congestion and crowding, number of accidents and casualties, energy consumption, pollution emissions, and user satisfaction.
\end{itemize}
It is often best to use some of each type of performance indicators. 

Another aspect to consider is the use of qualitative or quantitative data. Quantitative data refers to easy-to-measure information, while qualitative data refers to other types of information and they can be quantified using letter or number ratings. 

Relative indicators are often used to evaluate many impacts, such as trends or comparisons with peers. Reference units (also called ratio indicators) are measurement units normalized to facilitate comparisons, such as per-year, per-capita, per-mile, per-trip, per-vehicle-year and per euro. The selection of reference units can affect how problems are defined and solutions prioritized. For example, measuring impacts such as emissions, crashes and costs per vehicle-mile ignores the effects of changes in vehicle mileage. Measuring these impacts per-capita does account for changes in vehicle travel.
\newpage
Summing up the \emph{principles to consider selecting a new KPI} are:
\begin{itemize}
    \item Relevance to the community's definition of sustainability, considering the suburban or urban area
    \item Understandability by the community at large, not only experts
    \item Acceptance and usage by the community
    \item Long-term view of the community
    \item Integration of different relevant topic
    \item Based on information that is reliable, accessible, timely and accurate
    \item Consideration of local impacts at the expense of global impacts
    \item Quantitative KPIs are easier to analyze, they are considered more objective and they tends to receive more weight in a planning process. Sustainability indicators therefore require quantifying impacts as much as possible.
    \item Trade-off between smaller set of indicators, using available data, and larger set can be more comprehensive but have excessive data collection and analysis costs. 
\end{itemize}

\input{chapter/innovative_KPI/1_New_Technologies}
\input{chapter/innovative_KPI/2_Social_Sustainability}
\input{chapter/innovative_KPI/3_Green_Technologies}
\input{chapter/innovative_KPI/4_Manteinance}


